Notes and approaches to OCR

### 2020-12-01 outputs/documents/paper.Rmd
doc update and section three kindai

| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
Standard: $0.002 per trans      |                    |
| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
|	Kindai-OCR                           | Google    | Python Library | Free    |                    |

@@

@@

>>>>

| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
Standard: $0.002 per trans      |                    |
| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
|	Kindai-OCR                           | Result of n2i Project    | Python Library | Free    |                    |

@@

## Kindai-OCR

@@

In terms of flexibility...

Sequence of the characters...

Output given...xml, json, flat file, csv...

NUmber of characters well recognized...(Accuracy)
